Measuring Hash Trustworthiness via Collision Utility Metrics: Logical Cryptanalysis of MD4

### 2017-12-05 dsn-2018/bare_conf.tex
Change definition
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

Cryptographic hash functions form the core of many protocols which
trust that these functions preserve certain basic
properties. Cryptographic hash functions see widespread
use for file integrity checks to verify long term storage of
data, as cache invalidation techniques, and as a building block in network
protocols such as Kerberos and TLS.  The classes of functions suitable
for these use cases necessarily have
strong guarantees about properties of its members.
An ideal cryptographic hash has five main features: determinism - the
same message always results in the same hash; performability -
computing a hash for a message should not be algorithmically
difficult; non-reversibility - it should be infeasible to generate a message
from its hash except by trying all possible messages; sensitivity to
initial conditions - small changes to a message should change the hash
value to a degree that the new hash value appears uncorrelated with
the old hash value; unique digests - it should be infeasible to find
two different messages with the same hash value.

>>>>

Cryptographic hash functions form the core of many protocols which
trust that these functions preserve certain basic
properties. Cryptographic hash functions see widespread
use for file integrity checks to verify long term storage of
data, as cache invalidation techniques, and as a building block in network
protocols such as Kerberos and TLS.  The classes of functions suitable
for these use cases necessarily have
strong guarantees about properties of its members.
An ideal cryptographic hash has five main features: determinism - the
same message always results in the same hash; performability -
computing a hash for a message should not be algorithmically
difficult; non-reversibility - it should be infeasible to generate a message
from its hash except by trying all possible messages; sensitivity to
initial conditions - small changes to a message should change every bit of
the hash value with probability $\frac{1}{2}$;
unique digests - it should be infeasible to find two different messages with
the same hash value.
